### 2010-11-18 docs/tex/review.tex
Evolutionary Strategy.

\subsection{Evolutionary Strategies}

>>>>

\subsection{Evolutionary Strategies}
The key important property of these set of algorithms is \textbf{self-adaptation} of strategy parameters. The  parameters of Evolutionary Algorithm are included in the chromosomes and they co-evolve with the solution set while running the algorithm. To summarize these set of algorithms, they usually have real-valued vectors, their recombination process is discrete or intermediary, their mutation process uses Gaussian perturbation while parent selection is uniform random. In terms of their attribute feature they are fast and good optimizer for real-valued optimization.
